\documentclass[12pt]{article}
\usepackage{fancyhdr}
\usepackage{geometry}

% Set up page geometry
\geometry{a4paper, margin=1in}

% Header and Footer settings
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyhead[C]{Wonders of the Unknown World} % Header center
\fancyfoot[L]{Maulana Abul Kalam Azad University of Technology} % Footer left
\fancyfoot[R]{\thepage} % Footer right (page number)

\begin{document}

% Restore fancy page style after the title page
\thispagestyle{fancy}
\pagestyle{fancy}

% Section 1
\section{The Enchanted Forest}
Deep within the heart of the forest lies a hidden grove where time seems to stand still. Trees with silver leaves glow faintly in the moonlight, casting a serene light on the ground below. The air is thick with the scent of pine and earth, and if you listen closely, you can hear the soft murmur of the forest, as though the trees themselves are sharing an ancient, forgotten story. Those who enter this grove often leave with a sense of wonder, though none can truly explain the magic they felt.

% Section 2
\section{The Floating Isles}
High above the clouds, the floating isles drift silently through the sky. Massive chunks of land, suspended in the air, hold entire ecosystems within them—rivers, forests, and creatures long thought to be myth. Some say the isles are remnants of a lost world, while others believe they are the work of ancient technology beyond our understanding. Only a few have dared to journey to the isles, and their tales speak of unimaginable beauty and danger, where gravity seems to lose its hold, and the sky becomes the only limit.

\end{document}